### 2025-09-13 paper/sec/introduction.tex
More purging.

\subsection{Transparent Text}

Recent work on data provenance and data visualisation has shown how interactive provenance queries can be
supported automatically \cite{psallisas

\begin{itemize}
    \item Introduce basic idea, as complementary to transparent visualisations
\end{itemize}

>>>>

\subsection{Transparent Text via Interactive Provenance Queries}

Recent work on data provenance and data visualisation~\citep{psallidas18smoke,perera22,bond25} developed
software infrastructure for integrating interactive provenance queries into charts and figures. Visual outputs
like this, which here we call \emph{transparent visualisations}, allow readers to interact with a visual
elements and see the related data. In scientific papers, news articles and policy reports, charts and figures
usually only play a supporting role, however. The main claims are usually presented in natural language,
language which is rich with quantitative claims and allusions to data analyses which are not present in the
final artifact.

\rpnote{Small example here}
